Meta-analysis

### 2020-07-07 04_MetaAnalysis.Rmd
fixing the forestplot

Lets look at the trial variability in this model with a forest plot
```{r forestP, fig.height= 40, fig.width=10}
# If anyone knows how to fix the margins here it would be helpful!!!!!!!!!!!!!!!!
metafor::forest(PM_mv, cex =0.75 , width = 5,
                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, dat1$row_spacing, dat1$host_genotype, dat1$dose,
                             as.character(dat1$spray_management)),
                ilab.xpos = c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1),
                slab = NA, 
                xlim = c(-7, 3.5),
                ylim = c(4,119),
                xlab = "Grain yield mean difference")

@@

### add column headings to the plot
text(c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1), 117.9,cex = 0.85, 
     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose","SM"),
     font = 2)

>>>>

Lets look at the trial variability in this model with a forest plot
```{r forestP, fig.height= 25, fig.width=20}
polys <- data.frame(ref = names(coef(PM_mv)),
                    x = coef(PM_mv),
                    ci.lb = PM_mv$ci.lb,
                    ci.ub = PM_mv$ci.ub,
                    rows = c(112.8, 64.8, 22.8,93.5, 1.8))

metafor::forest(PM_mv, cex = 1.25 , width = 5,
                order = "fit",
                rows = c(126:114, 111:95, 92:66, 63:24, 21:3),
                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, 
                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
                ilab.xpos = c(-2.8, -2.2,-2.05,-1.95,-1.7,-1.5),
                slab = NA, 
                xlim = c(-3, 2.2),
                ylim = c(4,129),
                xlab = "Grain yield mean difference",
                addfit = FALSE,
                efac = c(0.5,2,0.2))

@@

### add column headings to the plot
text(c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5), 127.9,cex = 0.85, 
     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose"),
     font = 2)

addpoly(x = polys$x,
        ci.lb = polys$ci.lb,
        ci.ub = polys$ci.ub,
        col ="black",
        rows = polys$rows,
        cex = 1.3,
        efac = 0.2,
        font = "Arial Rounded MT Bold")
```
